Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2018-12-08 tex/WW4C_VHzQ.tex
WW4C_VHzQ .tex, .pdf udpated

Specifically, we use data from: 
\citet{Banados2014, Banados2016, Banados2018}, 
\citet{Becker2015}, 
\citet{Calura2014}, 
\citet{Carilli2007, Carilli2010}, 
\citet{Carnall2015}, 
\citet{Cool2006}, 
\citet{DeRosa2011}, 
\citet{Fan2000, Fan2001c, Fan2003, Fan2004, Fan2006, Fan2018}, 
\citet{Goto2006}, 
\citet{Ikeda2017}, 
\citet{Jiang2008, Jiang2009, Jiang2015},  
\citet{Kashikawa2015}, 
\citet{Koptelova2017}, 
\citet{Kim2015}, 
\citet{Kurk2007, Kurk2009}, 
\citet{Leipski2014}, 
\citet{Mahabal2005}, 
\citet{Matsuoka2016,  Matsuoka2018a, Matsuoka2018b},   
\citet{Mazzucchelli2017}, 
\citet{Morganson2012}, 
\citet{Mortlock2009, Mortlock2011},
\citet{McGreer2006, McGreer2013},  
\citet{Reed2015, Reed2017}, 
\citet{Stern2007},  
\citet{Tang2017}, 
\citet{Venemans2007, Venemans2012, Venemans2013, Venemans2015a, Venemans2015b, Venemans2016},
\citet{WangF2016, WangF2017, WangF2018a, WangF2018b},
\citet{Willott2007, Willott2009, Willott2010a, Willott2010b, Willott2013b, Willott2015}, 
\citet{Wu2015} 
\citet{YangJ2018}  
and 
\citet{Zeimann2011},

@@

\begin{table}
\begin{tabular}{l r l}
\hline  \hline
Survey              & \# VH$z$Qs & Notes/Survey reference  \\
\hline  
  ATLAS             &     4       &  \citet{Shanks2015} \\
  CFHQS            &   20       &  \citet{Willott2007} \\
  DELS               &     2       &  \citet{Dey2018} \\
  ELAIS              &     1       &  \citet{Vaisanen2000} \\
  FIRST              &     1       &  \citet{Becker1995} \\
  IMS                 &     1        &  \citet{Kim2015} \\
  MMT               &   12        &  \citet{McGreer2013} \\
  NDWFS           &     1         &  \citet{JD1999} \\
  PSO                 &   84         &   \citet{Kaiser2002, Kaiser2010} \\
  RD                   &     1         &  \citet{Mahabal2005} \\
  SDSS                & 156         & \citet{EDR} \\
  SDUV$^{a}$       &   20         & \citet{YangJ2017} \\
 SDWISE$^{b}$    &   27         &   \citet{WangF2016} \\
  SHELLQs         &  $^{c}$63   &  \citet{Matsuoka2016} \\  %% includes 8 objects from the first HSC paper..
  ULAS               &   10          & \citet{Lawrence2007} \\
  VDES              &   11          &  \citet{Reed2017} \\
  VIK                 &     9          &  \citet{Edge2013} \\
  VIMOS           &    1            &   \citet{LeFevre2003} \\
\hline  \hline
\end{tabular}
\caption{The number of VH$z$Q from given surveys, with the key survey or telescope reference.  
  $^{a}$SDUV  = SDSS+ULAS+VHS; 
  $^{b}$SDWISE = SDSS+WISE; 
  $^{c}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018} designation.}
      \label{tab:surveys}
\end{table}

@@

\appendix
\section{Filter Curves}\label{sec:filters} 
FRom the SVO Filter Profile Service\footnote{http://svo2.cab.inta-csic.es/svo/theory/fps/}.

@@

>>>>

Specifically, we use data from: 
\citet{Banados2014, Banados2016, Banados2018}, 
\citet{Becker2015}, 
\citet{Calura2014}, 
\citet{Carilli2007, Carilli2010}, 
\citet{Carnall2015}, 
\citet{Cool2006}, 
\citet{DeRosa2011}, 
\citet{Fan2000, Fan2001c, Fan2003, Fan2004, Fan2006, Fan2018}, 
\citet{Goto2006}, 
\citet{Ikeda2017}, 
\citet{Jiang2008, Jiang2009, Jiang2015},  
\citet{Kashikawa2015}, 
\citet{Koptelova2017}, 
\citet{Kim2015, Kim2018},  
\citet{Kurk2007, Kurk2009}, 
\citet{Leipski2014}, 
\citet{Mahabal2005}, 
\citet{Matsuoka2016,  Matsuoka2018a, Matsuoka2018b},   
\citet{Mazzucchelli2017}, 
\citet{Morganson2012}, 
\citet{Mortlock2009, Mortlock2011},
\citet{McGreer2006, McGreer2013},  
\citet{Reed2015, Reed2017}, 
\citet{Stern2007},  
\citet{Tang2017}, 
\citet{Venemans2007, Venemans2012, Venemans2013, Venemans2015a, Venemans2015b, Venemans2016},
\citet{WangF2016, WangF2017, WangF2018a, WangF2018b},
\citet{Willott2007, Willott2009, Willott2010a, Willott2010b, Willott2013b, Willott2015}, 
\citet{Wu2015} 
\citet{YangJ2018a, YangJ2018b}  
and 
\citet{Zeimann2011},

@@

\begin{table}
\begin{tabular}{l r l}
\hline  \hline
Survey              & \# VH$z$Qs & Notes/Survey reference  \\
\hline  
  ATLAS             &     4       &  \citet{Shanks2015} \\
  CFHQS            &   20       &  \citet{Willott2007} \\
  DELS               &   16       &  \citet{Dey2018} \\
  ELAIS              &     1       &  \citet{Vaisanen2000} \\
  FIRST              &     1       &  \citet{Becker1995} \\
  HSC                 &    8        & \citet{Miyazaki2018} \\
  IMS                 &     5        &  \citet{Kim2015} \\
  MMT               &   12        &  \citet{McGreer2013} \\
  NDWFS           &     1         &  \citet{JD1999} \\
  PSO                 &   83         &   \citet{Kaiser2002, Kaiser2010} \\
  RD                   &     1         &  \citet{Mahabal2005} \\
  SDSS                &  170         & \citet{EDR} \\
  SDUV$^{a}$       &   20         & \citet{YangJ2017} \\
 SDWISE$^{b}$    &   27         &   \citet{WangF2016} \\
%  SHELLQs         &  $^{c}$63   &  \citet{Matsuoka2016} \\  %% if you include 8 objects from the first HSC paper...
  SHELLQs         &    55         &  \citet{Matsuoka2016}     \\  
  UHS               &    1            &  \citet{Fan2018} \\
  ULAS               &   10          & \citet{Lawrence2007} \\
  VDES$^{c}$              &   17          &  \citet{Reed2017} \\
  VIK                 &     9          &  \citet{Edge2013} \\
  VIMOS           &    1            &   \citet{LeFevre2003} \\
\hline  \hline
\end{tabular}
\caption{The number of VH$z$Q from given surveys, with the key survey or telescope reference.  
  $^{a}$SDUV  = SDSS+ULAS+VHS; 
  $^{b}$SDWISE = SDSS+WISE; 
  $^{c}$VDES = VHS/VIKING+DES; 
%  $^{c}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018} designation.
}
      \label{tab:surveys}
\end{table}

@@

\appendix
%\section{Filter Curves}\label{sec:filters} 
%From the SVO Filter Profile Service\footnote{http://svo2.cab.inta-csic.es/svo/theory/fps/}.

@@

%% \section{Notes on Individual Objects}
%% \input{/cos_pc19a_npr/data/highest_z_QSOs/notes_on_individual_objects}
